Accelerated evolution of convective simulations

### 2018-02-15 tex/bvp_paper.tex
rough draft of new words is in

\begin{document}
\author{Evan H. Anders}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Benjamin P. Brown}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Jeffrey S. Oishi}
\affiliation{Department of Physics and Astronomy, Bates College, Lewiston, ME 04240, USA}
\title{Accelerated convergence of convective simulations using boundary value problems}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/time_trace.png}
\caption{Traces of system energies vs. time for a long thermal rundown (a) and BVP convergence
(b) are shown for $S = 10^{4 + 2/3}$.  The horizontal extent of the subplots is set
such that one simulation time unit takes up an equal amount of paper space in (a) and (b). Volume averaged
kinetic energy is shown in black, and the volume averaged temperature with the top value removed, is shown
in red.
The dashed vertical line on (a) represents the time at which averaging begins in the BVP solution in (b),
and the horizontal dashed lines show the equilibrium value of the energies. The blue vertical lines represent
the beginning of the time-averaging window.
(c) System fluxes early in the run (the orange highlights in (a)) are shown.  
Black is the sum of the flux, purple
is the convective flux, and red is the conductive flux.
(d) Fluxes in the converged rundown IVP compared to the converged BVP.  The sum of flux is shown in
black \& grey, the convective flux is shown in purple \& pink, and the conductive flux is shown in red \& orange.
(e) The differences between the BVP and rundown fluxes is shown.  While not in perfect agreement, 
the BVP fluxes deviate from the rundown fluxes by only a few percent of the total flux, and
are much closer to the converged state than the initial fluxes, as in (c).
\label{fig:time_trace} }
\end{figure}

@@

@@

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Scaling plots are shown for the Nusselt number (a), the
Reynolds number (b), and the volume-averaged temperature (c).  
Symbols represent the mean value of
a measurement, vertical lines represent the standard deviation of the measurement over the
time window, and error bars represent the shift in the mean value over the window.
(a) Nu, which measures heat transport, scales roughly like $Ra^{1/5}$, and above Ra$\geq 10^6$,
simulations display horizontally oscillating plumes which have oscillating periods of high transport
and low transport.  The mean value is marginally diminished as a result, and the variance of Nu with time
is large. (b) Re, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$ in 2D and is not distinctly different in 3D. (c) The average temperature flucutation, minus the top
temperature, which is a scalar measure of the final average thermodynamic state and should approach zero
in the limit of infinitely large Ra.
The temperature profile is slow to adjust, and differences between
BVP solutions and rundown solutions are quite easy to pick out in this measure. (d-f)
Relative error is shown between the BVP and IVP measurements of Nu (d), Re (e), and the
mean temperature (f). The grey box indicates the region in which only BVP runs were
carried out due to computational expense.
\label{fig:parameter_space_comparison} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of a BVP solution and a long IVP rundown at
$S = 10^{5}$ are shown.  (a) Evolved temperature profiles, as a function of height.
(b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
(c) Probability distributions of point-by-point measurements of $T$ throughout the two domains over the
averaging windows are shown.  The cumulative distribution functions are overplotted and the maximum
difference between them in 0.0407. This difference arises due to the imperfect alignment of the
mean domain temperatures, but it is clear that otherwise the statistics are quite similar.
\label{fig:temp_comparison} }
\end{figure}

@@

Despite differences between the SE and AE solutiosn for the case studied in 
Figs. \ref{fig:time_trace}, \ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison},
the AE method is still extremely powerful.  The first application of the AE method
($t \approx 70$ in Fig. \ref{time_trace}b) immediately increases the 
average time step of our solver by a factor of 2-3. At higher supercriticality
($S = 10^7$), the AE solve immediately boosts the timestep by nearly a factor of 4.
Thus, not only does this method evolve the solution into nearly the correct state, 
but further time evolution (either to achieve precisely the correct thermodynamic
state or to take measurements of fluid quantities) happens more efficiently.

\section{Discussion \& Conclusions}
\label{sec:discussion}
The method presented here is a first step towards taking meaningful measurements
of highly turbulent convection on manageable, human timescales.  As demonstrated in Figs.
1-4, this BVP method quickly converges simulations to within a few percent of the true final
state. Furthermore, the total simulation time required to use the BVPs does not change drastically from
low $S$ to high $S$, so the main prohibition on high Ra states is the difficulty of timesteps becoming
increasingly small as turbulence increases.  Additionally, post-BVP, we generally see an increase of the
timestep size by nearly a factor of two due to the less intense driving of the near-converged state that
is achieved quickly.

It is important to note that the measurements made in
this paper were generally done for short timescales (a few hundred buoyancy times) in
order to show the precise differences between the BVP solutions and the IVP solutions.
Where there are differences, the BVP solution is trending towards the IVP solution,
and if measurements were taken over long timescales (e.g., a thermal time), the
differences between the BVP solution and IVP solution would be negligible.

One major benefit of the BVP method used here is that it preserves the natural behavior of 
the convective solution (such as the horizontally oscillatory rolls
of high-Ra 2D states in Fig. \ref{fig:parameter_space_comparison}).
One frequently used method of measuring dynamics in high-Ra simulations is that of bootstrapping,
in which the converged solution of a low-Ra state is used as initial conditions for a higher-Ra
simulation.  While this method is powerful, it can be influenced by hysteresis effects,
and the steady rolls achieved at low Ra can result in an artifically over-stable high-Ra
roll solution.  The BVP method we present here uses random noise initial conditions which allows the
convective solution to naturally choose the dynamics.

Another benefit of our BVP method is that it can be easily extended to more complicated
configurations.  For example, to use this method in simulations of stratified compressible convection,
one need only adapt the BVP equations to the appropriate equations of hydrostatic equilibrium
and thermal equilibrium obtained by averaging the fully compressible, ideal gas
steady state momentum and energy equations \cite{anders&brown2017, lecoanet&all2014}.
In compressible convection, where the density is allowed to change,
it is also essential to conserve mass by adding boundary conditions on the integrated mas density at
the upper and lower boundaries, much as stellar structure codes do \cite{paxton&all2011}.

While we have not chosen to use them here, this BVP method can be extended to other boundary conditions.  
To solve for fixed temperature boundary conditions, the 
main difficulty is in finding the amount of flux through the system, $F_{\text{tot, steady}}$.
However, by knowing the averaged value of the conductive flux (from the boundary conditions)
and the ratios in Eqn. (\ref{eqn:bvp_ratios}), $F_{\text{tot, steady}}$ can be found.
In the case of
fixed flux boundary conditions, the temperature solution is degenerate.
However, using knowledge about the system -- such as the initial symmetry of the
RB state around $T = 0$, the final solution can be pegged onto the proper profile.

Future work will aim to apply the methods presented here to compressible systems,
internally heated systems, and systems with more complex forms of the conductive flux.

@@

\appendix
\section{Table of Runs}
\label{appendix:run_table}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X X X X X X}
\hline															
$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{rundown}}$	&	Nu$_{\text{BVP}}$	\\
\hline															
$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	128	&	$52.8$	&	100	&	(TBD)	&	(TBD)	\\
$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	128	&	$77.6$	&	100	&	--	&	--	\\
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	128	&	$114$	&	100	&	--	&	--	\\
$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	128	&	$167$	&	100	&	--	&	--	\\
$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	128	&	$245$	&	100	&	--	&	--	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	256	&	$360$	&	100	&	--	&	--	\\
$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	256	&	$528$	&	100	&	--	&	--	\\
$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	256	&	$776$	&	100	&	--	&	--	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	512	&	$1.14 \cdot 10^3$	&	200	&	--	&	--	\\
$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	512	&	$1.67 \cdot 10^3$	&	500	&	--	&	--	\\
$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	1024	&	$2.45 \cdot 10^3$	&	500	&	--	&	--	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	1024	&	$3.60 \cdot 10^3$	&	500	&	--	&	--	\\
$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	1024	&	$5.28 \cdot 10^3$	&	500	&	--	&	--	\\
$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	1024	&	$7.76 \cdot 10^3$	&	500	&	--	&	--	\\
$10^5$	&	$1.30 \cdot 10^8$	&	512	&	2048	&	$1.14 \cdot 10^4$	&	500	&	--	&	--	\\
$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	2048	&	$1.67 \cdot 10^4$	&	500	&	--	&	--	\\
$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	2048	&	$2.45 \cdot 10^4$	&	500	&	--	&	--	\\
$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	4096	&	$3.60 \cdot 10^4$	&	500	&	--	&	--	\\
\hline															
\end{tabularx}
\end{center}

\section{Accelerated Evolution Recipe}
\label{appendix:recipe}
In general, the BVP solve is completed in the following steps:
\begin{enumerate}
\item Run the convective IVP. Once the convection achieves a volume-averaged Re of $\sqrt{\text{Ra}/\text{Ra}_{\text{crit}}}$,
wait for 50 freefall time units.  
\item Start taking the averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$, waiting either
30 freefall time units or until the average profiles change by no more than 1 part in 1000 on a
given timestep, whichever is a more difficult criterion. This ensures that
the profiles being used in the BVP are steady and smooth, and that they sample the full behavior of the convection.
\item Construct $\angles{w T_1}_{\text{steady}}$, $\xi$, and $\angles{\bm{u}\times\bm{\omega}}_{\text{steady}}$
from the flux profiles.
\item Solve for $\angles{T_1}$ and \angles{\varpi} of the
evolved state.  Adjust the mean profiles in the IVP.
\item Multiply the velocity field and the fluctuations in $T_1$ about its horizontal average by $\sqrt{\xi}$ in the IVP. 
\item Continue running the IVP for freefall 50 time units to allow for the velocities to equilibrate to their new background state.
\item Repeat steps 2-6 to complete a second BVP and get closer to the right solution now that we
are far from the very unstable transient period.
\item Take averages for the amount of time specified for the given run in Appendix \ref{section:appendix_table}.
\end{enumerate}

>>>>

\begin{document}
\author{Evan H. Anders}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Benjamin P. Brown}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Jeffrey S. Oishi}
\affiliation{Department of Physics and Astronomy, Bates College, Lewiston, ME 04240, USA}
\title{Accelerated evolution of convective simulations}

@@

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/time_trace.png}
\caption{Traces of kinetic energy and mean temperature vs. time for a (a) SE and (b)
AE run are shown at $S = 10^5$.
The horizontal extent of the plots is set
such that one simulation time unit takes up an equal amount of paper space in (a) and (b).
The mean evolved values are shown as horizontal dashed lines.
(c) System fluxes shortly after the convective transient are shown, at times corresponding
to the orange highlighting in (a) and (b).  The sum of the flux is shown in black,
the convective flux is shown in purple, and the conductive flux is shown in red.
(d) Fluxes in the evolved AE state are shown, measured during the time highlighted
in green in (b).  
(e) The difference between the AE and SE fluxes, measured over the green highlighted
regions in (a) and (b), are shown.
Note that the black dashed vertical line in (a) denotes the simulation time at which
averaging begins for the AE solution shown in (b).
\label{fig:time_trace} }
\end{figure}

@@

The AE method specified here quickly converges the fluxes within the
system to within a few percent of the fluxes in a system converged through
SE (Fig. \ref{fig:time_trace}d \& e).

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement, while vertical lines represent the standard deviation of the measurement,
showing natural variation over the
averaging window, and error bars represent the change in the mean value over the window,
such that large error bars would represent a poorly converged solution.
(a) The Nusselt number scales as $Ra^{1/5}$, and above S$\geq 10^{3+2/3}$,
simulations exhibit oscillating plume structures whose heat transport varies over time.  
(b) The RMS Reynolds number, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$. (c) Temperature, with its value at the upper boundary removed, is shown.
Relative error for (d) Nu, (e) Re, and (f) $T$ are shown between measurements 
taken in AE solutions and SE solutions.
The greyed area of the plot indicates the region in which only AE runs were
carried out due to computational expense. The run at $S = 10^5$ marked as a
black square is examined in more details in Figs. \ref{fig:time_trace},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
\label{fig:parameter_space_comparison} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
at $S = 10^{5}$ are shown.  (a) Evolved temperature profiles, as a function of height.
(b) The percentage difference between the temperature profiles as a function of height.
(c) Probability distributions of point-by-point measurements of the temperature field.
$T$ is sampled every 0.1 time units for 500 total time units,
and was interpolated onto an evenly spaced grid before sampling.
The cumulative distribution function is overplotted on each plot. 
\label{fig:temp_comparison} }
\end{figure}

@@

Despite differences between the SE and AE solutions for the case studied in 
Figs. \ref{fig:time_trace}, \ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison},
the AE method is still extremely powerful.  The first application of the AE method
($t \approx 70$ in Fig. \ref{time_trace}b) immediately increases the 
average time step of our solver by a factor of 2-3. At higher supercriticality
($S = 10^7$), the AE solve immediately boosts the timestep by nearly a factor of 4.
Thus, not only does this method evolve the solution into nearly the correct state, 
but further time evolution (either to achieve precisely the correct thermodynamic
state or to take measurements of fluid quantities) happens more efficiently.

\section{Extensions of the AE method}
\label{section:extensions}
Here we have used \RB convection as a test case for the AE method, but we argue that
the true power of this method is in its extensions to more complicated studies.
Such extensions are beyond the scope of this work, but we will briefly describe
avenues in which extensions to the AE method will be useful.
For example, in studies of stratified convection where the thermal diffusivity
is inversely proportional to the density \cite{anders&brown2017}, AE solutions
will allow for the careful study of a broader range of parameter space. 
Further, in studies where stable and convecting regions are paired
\cite{hurlburt&all1986, couston&all2017}, the stable layers cannot rely on convective
motions to restratify them and instead evolve on the order of the slow thermal
timescale. In
fully-convective domains, such as those studied here, the atmosphere evolves
much more rapidly than the thermal diffusion time (see e.g., Fig. \ref{fig:time_trace}a).

We note also that a further strength of the AE method is its generality.  One
need only derive the steady-state, horizontally-averaged equations for a given
equation set (e.g., Eqns. \ref{eqn:bouss_BVP_momentum} \& \ref{eqn:bouss_BVP_energy})
and couple that information with knowledge of the current dynamics (Eqn. \ref{eqn:bvp_ratios})
and the boundary conditions. Thus this method can be easily applied to more complex
systems, and merely require that the experimenter understand the energy transport
present in their systems.

We have only studied solutions in which we use mixed thermal boundary conditions,
as in Eqn. \ref{eqn:bcs}. However, this method can be easily applied to fixed-temperature
boundary conditions, as well.  Rather than knowing the total final flux (F$_{\text{bot}}$)
through the system a priori, it must be measured using the ratios in
Eqn. \ref{eqn:bvp_ratios}.  We hesitate to use the AE method for systems in which
both boundaries fix the flux, as such systems have degenerate solutions for the temperature.

\section{Conclusion}
\label{sec:discussion}
Here we have described a method for converging convective simulations using
a method of Accelerated Evolution (AE), and compared it to Standard
Evolution (SE) achieved by running simulations for a thermal timescale.
We have shown that the AE method produces dynamics that are similar to SE
dynamics on much shorter timescales, and have discussed differences that arise
between the two methods.

We have shown that the AE method is valid at low values of $S$, in which solutions
converge quickly, and at high values of $S$, at which SE solutions can take an
intractable amount of time.  This shows that the AE method not only progresses
solutions towards the correct evolved state (at high $S$), but it also does not
throw the simulation out of the correct evolved state (at low $S$).  We have studied
the AE method in both 2D and 3D, but since the method relies fundamentally on
1D information from the transient flows, we have restricted most of our study
to 2D and merely demonstrated the method's efficacy in 3D, too.

This work serves as a first step towards creating robust methods for
achieving evolved convective solutions at high Ra on short timescales.
Future studies will extend this method to stratified, fully compressible
convection \cite{anders&brown2017}, and to systems with internal heating.

@@

\appendix
\section{Accelerated Evolution Recipe}
\label{appendix:recipe}
In order to achieve Accelerated Evolution (AE), we solve a 1D Boundary Value Problem
consisting of Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}).
There are a steps required to properly advance the solution are as follows:
\begin{enumerate}
\item Update averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$
every timestep.  Wait until that average converges. To ensure that an average is converged, at
least some time $t_{\text{min}}$ must have passed since the average was started, and
the profiles must change by no more than $P$\% on a given timestep.
\item Construct F$_\text{conv, ev}$ and $\xi$ as specified in section \ref{subsection:ae}.
\item Solve for $\angles{T_1}_{x,y}$ and $\angles{\varpi}_{x,y}$ of the
evolved state.  Adjust the profiles in the convecting simulation accordingly
\item Multiply the velocity field and the fluctuations in $T - \angles{T}_{x,y}$ by $\sqrt{\xi}$ in the IVP. 
\item Continue running the simulation.
\end{enumerate}
We refer to this process as an ``AE BVP solve.''

In general, we find that repeating this method multiple times is the best way to
ensure that the AE solution is truly converged. For all runs in 2D at $S < 10^5$, we
waited for 50 time units after peak transient, completed an AE BVP solve
with $t_{\text{min}} = 30$ and $P = 0.1$, waited 50 more time units, and then
did a second AE BVP solve with the same parameters.
For all 3D runs and 2D runs in the range $S \in [10^5, 10^6]$,
we waited 20 time units after peak transient, completed an AE BVP solve
with $t_{\text{min}} = 20$ and $P = 1$ in order to quickly reach a near-
converged state and vastly increase our timestep.  After this, we completed
two AE BVP solves, separated by 30 time units each, with $t_{\text{min}} = 30$
and $P = 0.1$ to get very close to the solution (as in Fig. \ref{fig:time_trace}b).
At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
$P = 1$, waiting 20 time units after peak transient and 30 time units between
the two solves.

\section{Table of Runs}
\label{appendix:run_table}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X X X X X X X }
\hline																	
$S$	&	Ra	&	nz	&	nx, ny	&	3D	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
\hline																	
$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	FALSE	&	$52.8$	&	100	&	1.46	&	1.46	\\
$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	FALSE	&	$77.6$	&	100	&	1.95	&	1.95	\\
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	FALSE	&	$114$	&	100	&	2.43	&	2.42	\\
$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	FALSE	&	$167$	&	100	&	2.54	&	2.54	\\
$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	FALSE	&	$245$	&	100	&	3.14	&	3.14	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	FALSE	&	$360$	&	100	&	3.8	&	3.8	\\
$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	FALSE	&	$528$	&	100	&	4.71	&	4.71	\\
$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	FALSE	&	$776$	&	100	&	5.5	&	5.5	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	FALSE	&	$1.14 \cdot 10^3$	&	200	&	6.4	&	6.33	\\
$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	FALSE	&	$1.67 \cdot 10^3$	&	500	&	6.87	&	6.95	\\
$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	FALSE	&	$2.45 \cdot 10^3$	&	500	&	7.54	&	7.59	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	FALSE	&	$3.60 \cdot 10^3$	&	500	&	8.83	&	8.83	\\
$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	FALSE	&	$5.28 \cdot 10^3$	&	500	&	10.13	&	10.14	\\
$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	FALSE	&	$7.76 \cdot 10^3$	&	500	&	11.65	&	11.69	\\
$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	FALSE	&	$1.14 \cdot 10^4$	&	500	&	14.02	&	14.18	\\
$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	FALSE	&	$1.67 \cdot 10^4$	&	500	&	N/A	&	16.21	\\
$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	FALSE	&	$2.45 \cdot 10^4$	&	500	&	N/A	&	18.58	\\
$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	FALSE	&	$3.60 \cdot 10^4$	&	500	&	N/A	&	22.132	\\
$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	FALSE	&	$1.14 \cdot 10^5$	&	200	&	N/A	&	TBD	\\
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64,64	&	TRUE	&	$114$	&	100	&	2.42	&	2.42	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128,128	&	TRUE	&	$360$	&	100	&	3.97	&	4	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256,256	&	TRUE	&	$1.14 \cdot 10^3$	&	500	&	6.27	&	6.27	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512,512	&	TRUE	&	$3.60 \cdot 10^3$	&	500	&	9.92	&	9.88	\\
\hline																	
\end{tabularx}
\end{center}
